### 2022-08-02 README.Rmd
funding information added
setting up tinytex in github action

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).

>>>>

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. The core computational routines are implemented with the [Eigen](https://eigen.tuxfamily.org/index.php?title=Main_Page) C++ library and [RcppEigen](https://cran.r-project.org/package=RcppEigen) interface, with OpenMP for parallel computation. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206). This work was supported by the U.S. National Science Foundation under Grants No. [SES-1921523](https://nsf.gov/awardsearch/showAward?AWD_ID=1921523) and [DMS-2015552](https://nsf.gov/awardsearch/showAward?AWD_ID=2015552).
